### 2025-02-19 paper/paper.tex
Included slight changes to severe case
Finished editing Sections 5 & 6

\paragraph{Dataset and Methodology} \ \

@@

To evaluate the effectiveness of different regression techniques under this structure, we compare Principal Component Regression (PCR) and Partial Least Squares (PLS). The high multicollinearity present in NIR spectra makes it necessary to use dimensionality reduction techniques. PLS, due to its supervised nature, selects components that maximize covariance with the response variable, while PCR, which is unsupervised, requires a slightly larger number of components to reach a similar level of predictive performance.

A detailed decomposition of Mean Squared Error (MSE) into its bias and variance components in our simulations illustrates the advantage of using dimensionality reduction (Figure 3). PCR and PLS significantly reduce variance by selecting fewer components, thereby achieving much lower MSE. However, at their optimal component selection points, both PCR and PLS still introduce some bias as a trade-off for reduced variance. This bias, however, is minimal compared to the large variance that would be present if no dimensionality reduction were applied, making PCR and PLS the most suitable approaches for this type of high-dimensional regression problem.

@@

\section{Outlook: Limitations and Possible Extensions}

\subsection{Limitations of This Study}

@@

\paragraph{Assumptions on Data Distribution} \ \
The study assumes predictor variables follow a normal distribution, whereas real-world data often exhibit skewness, heavy tails, or heteroscedasticity. Since PCR and PLS rely on linear transformations, their performance may degrade under non-Gaussian conditions. Future work could explore robust versions incorporating transformations (e.g., Box-Cox) or heteroscedasticity-aware adaptations.

\paragraph{Limited Exploration of Nonlinear Relationships} \ \
PCR and PLS assume linearity between predictors and response variables, limiting their applicability in complex settings like genomics or finance. Nonlinear alternatives, such as Kernel PCA, Kernel PLS, and Deep PLS, could improve predictive power. Future research should evaluate these methods in high-dimensional, nonlinear contexts.

\subsection{Possible Extensions and Future Research Directions}

\paragraph{Hybrid Approaches Combining PCR and PLS} \ \
A hybrid model could integrate PCR’s variance-maximizing properties with PLS’s covariance-maximization to enhance predictive performance. Ensemble-based PCR-PLS approaches may further improve regression outcomes.

\paragraph{Integration with Machine Learning} \ \
PCR and PLS could be used as feature extraction methods for machine learning models like Random Forests, SVMs, or Neural Networks. Additionally, incorporating PLS-based features into gradient boosting models (e.g., XGBoost, LightGBM) could improve performance in structured data applications.

\paragraph{Sparse and Robust PLS Variants} \ \
Sparse PLS (SPLS) introduces sparsity constraints for improved interpretability, while Robust PLS (RPLS) enhances resilience to outliers and non-Gaussian noise. Optimizing these methods for high-dimensional data remains a promising direction.

\paragraph{Bayesian Extensions} \ \
Bayesian PCR (BPCR) and Bayesian PLS (BPLS) integrate probabilistic frameworks, improving uncertainty quantification and robustness in small-sample settings. These extensions could be valuable in bioinformatics, finance, and environmental modeling.

\paragraph{Functional PCR and PLS} \ \
For time-series, spectral, and medical imaging data, Functional PCR (fPCR) and Functional PLS (fPLS) extend traditional methods to functional data analysis. Future research could apply these approaches in fields like climate modeling and EEG analysis.  
\newpage

>>>>

\paragraph{Dataset description} \ \

@@

@@

\section{Limitations and Possible Extensions}

@@

\paragraph{Assumptions on Data Distribution} \ \

The study assumes predictor variables follow a normal distribution, whereas real-world data often exhibit skewness, heavy tails, or heteroscedasticity. Since PCR and PLS rely on linear transformations, their performance may degrade under non-Gaussian conditions. Future work could explore robust versions incorporating transformations (e.g., Box-Cox) or heteroscedasticity-aware adaptations.

\paragraph{Limited Exploration of Nonlinear Relationships} \ \

PCR and PLS assume linearity between predictors and response variables, limiting their applicability in complex settings like genomics or finance. Nonlinear alternatives, such as Kernel PCA, Kernel PLS, and Deep PLS, as well as Functional PCR and Functional PLS could improve predictive power. Future research should evaluate these methods in high-dimensional, nonlinear contexts.
